Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-21 paper/paper.tex
problem space changes

To store a model or a collection's models, a new instance method has been added
to the Backbone.Model and Backbone.Collection options called
``\verb=saveToStore=''. For models, this method simply saves the model's
attributes to the localStorage. For collections, this method uses the
persistence strategy identified by the collection to save the sorted list of
models into the localStorage. To load the data for a model or collection from
localStorage, a new method called ``\verb=loadFromStore='' has been added to
Backbone.Model and Backbone.Collection. For models, this simply loads the data
from localStorage into the model; for collections; this method identifies the
persistence strategy used by the collection and uses the correct retrieval
method to fetch the data from localStorage, parse it back into an array of
models, and add them to the collection.

@@

Our project makes two main contributions. First, we present an API that
automates local caching for web applications. This API will allow developers to
choose from two storage strategies for locally cached data:

@@

We find that our API provides superior load performance for data
stored locally vs.\ remotely under all data sizse and quantity conditions except
for the case of loading many small items. Furthermore, we find that our
implementation of local caching exhibits the greatest speedup when data is
stored using the first strategy, with one key-value pair per collection. This
suggests that local caching is most advantageous for applications that load
data of larger size, and moderate to large quantity.

@@

To evaluate the benefits of Backbone-store, we built three test applications to
understand how our solution handled three different sizes of items requiring
storage. To test large items that might represent a document, we used five
paragraphs of Lorem ipsum, totaling 3265 characters per item (~3200 bytes). To examine
medium size items such as emails, we used one paragraph of Lorem ipsum,
totaling 905 characters per item (~900 bytes) . To examine smaller items such as personal
notes, we used a short string of 70 characters (~70 bytes). These character lengths are the
length of the JSON string that represents each item. The three applications
performed the same task: 
\begin{enumerate}
\item load some number of a particular type of item (e.g., doc, email, note) from
local storage
\item load some number of a particular type of item (e.g., doc, email, note) from the server
\item record the load time.
\end{enumerate}

@@

This report described our extension for the Backbone.js library, which
simplifies the task of persisting a collection of data models to a web
browser's local storage, in order to facilitate faster load times and reduced
server load. This extension provides an API to facilitate saving and loading
collections on demand, using one of two different persistence strategies. We
tested our extension using three different demo applications, with different
characteristics for the data that is being used by the application. Our tests
varied both the number of data items in a single collection and the size of
each data itme, to simulate a number of different application scenarios. Our
tests showed that our extension is effective at reducing the load times in many
different scenarios, resulting in an improved experience for the application
user.

>>>>

To store a model or a collection's models, a new instance method has been added
to the Backbone.Model and Backbone.Collection options called
``\verb=saveToStore=''. For models, this method simply saves the model's
attributes to the localStorage. For collections, this method uses the
persistence strategy identified by the collection to save the sorted list of
models into the localStorage. To load the data for a model or collection from
localStorage, a new method called ``\verb=loadFromStore='' has been added to
Backbone.Model and Backbone.Collection. For models, this simply loads the data
from localStorage into the model; for collections, this method identifies the
persistence strategy used by the collection and uses the correct retrieval
method to fetch the data from localStorage, parse it back into an array of
models, and add them to the collection.

@@

Our project makes two main contributions. First, we create an API that
automates local caching for web applications. This API will allow developers to
choose from two persistence strategies for locally cached data:

@@

@@

To evaluate the benefits of Backbone-store, we built three test applications to
understand how our solution handled three different sizes of items requiring
storage. To test large items that might represent a document, we used five
paragraphs of Lorem ipsum, totaling 3265 characters per item (~3200 bytes). To examine
medium size items such as emails, we used one paragraph of Lorem ipsum,
totaling 905 characters per item (~900 bytes) . To examine smaller items such as personal
notes, we used a short string of 70 characters (~70 bytes). These character lengths are the
length of the JSON string that represents each item. The three applications
performed the same task: 
\begin{enumerate}
\item Load some number of a particular type of item (e.g., doc, email, note) from
local storage
\item Load some number of a particular type of item (e.g., doc, email, note) from the server
\item record the load time.
\end{enumerate}

@@

This report describes our extension for the Backbone.js library, which
simplifies the task of persisting a collection of data models to a web
browser's local storage, in order to facilitate faster load times and reduce
server load. This extension provides an API to facilitate saving and loading
collections on demand, using one of two different persistence strategies. We
test our extension using three different demo applications, with different
characteristics for the data that are being used by the application. Our tests
vary both the number of data items in a single collection and the size of
each data item, to simulate a number of different application scenarios. Our
tests show that our extension is effective at reducing the load times in many
different scenarios, resulting in an improved experience for the application
user.
